Mapping malaria by sharing spatial information between incidence and prevalence datasets

### 2019-09-06 ms.tex
Fix table (somehow) and andre edits.

The linear predictor is composed of an intercept, $b_0$, covariates, $X$, and a vector of regression coefficients $\boldsymbol\beta$.
We also include a spatial, Gaussian random field, $u(s, \rho, \sigma_u)$ and a polygon-level iid random effect, $ v_a(\sigma_v)$.
$$\eta_b = \beta_0 + \boldsymbol\beta X  + u(s, \rho, \sigma_u) + v_a(\sigma_v) $$
The Gaussian spatial effect $u(s, \rho, \sigma_u)$ has a Mat\'ern covariance function and two hyper parameters: $\rho$, the nominal range on the longitude-latitude scale (beyond which correlation is $< 0.1$) and $\sigma_u$, the marginal standard deviation.
The iid random effect, $v_a \sim \operatorname{Normal}(0, \sigma_v)$,  was grouped by polygon, with all pixels within polygon $j$ being grouped together.
Internally, this effect is parameterised as the log of the precision, $\omega_v = \log(\tau_v) = \log(\frac{1}{{\sigma_v}^2})$ to improve numeric stability.
This random effect modelled both missing covariates and extra-Poisson sampling error.

@@

We assigned $\sigma_v$ a penalised complexity prior \citep{simpson2017penalising} such that $P(\sigma_v > 0.05) = 0.0000001$.
This was based on a comparison of the variance of Poisson random variables, with rates given by the number of cases observed, and an independently derived upper and lower bound for the case counts using the approach defined by Cibulskis and colleagues \citep{cibulskis2011worldwide}.
We found that an iid effect with a standard deviation of 0.05 was able to account for the discrepancy between the assumed Poisson error and the independently derived error.

@@

$$\eta_b = \beta_0 + \mathbf{1}_p\beta_p +  \boldsymbol\beta X  + u(s, \rho, \sigma_u) + v_a(\sigma_v) + w_b(\sigma_w).$$
As well as the global intercept, $\beta_0$, this model has a prevalence survey specific intercept $b_p$ where the indicator function, $\mathbf{1}_p$ denotes that this term is zero except when a prevalence point-survey is being considered.
The iid random effect, $v_a \sim \operatorname{Norm}(0, \sigma_v)$, was again grouped by polygon, with all pixels and point-surveys within polygon $a$ being in the same group as polygon $a$.
The second iid random effect, $w_b \sim \operatorname{Normal}(0, \sigma_w)$, was applied to each point-survey.
To improve numeric stability this effect is also parameterised internally as the log of the precision, $\omega_w = \log(\tau_w) = \log(\frac{1}{{\sigma_w}^2})$.
This effect modelled extra-binomial sampling noise.
As such, this random effect is not included in the predicted uncertainty in the incidence or prevalence layers.

@@

@@

\begin{table}
\caption{\label{table1}
Summary of out-of-sample accuracy for all cross-validation experiments. 
Mean absolute error of predicted incidence rate against out-of-sample observed data for three countries.}
\centering
\fbox{%
\begin{tabular}{lllll}
\hline
{\bf Cross-validation} & {\bf Country}  & {\bf Baseline} & {\bf Prev GP} & {\bf Joint} \\
\hline 
Random & Indonesia  & 13.95 &  14.09 &  {\bf 13.79}\\
& Senegal  & 12.41 &  {\bf 12.37} &  13.07\\
& Madagascar  & 39.06 &  {\bf 35.82} &  36.36\vspace{3mm}\\
Spatial & Indonesia & {\bf 14.77} &  {\bf 14.77} &  16.46\\
& Senegal  & 13.09 &  {\bf 12.21} &  15.15\\
& Madagascar & 67.73 &  50.38 &  {\bf 44.05}\\
\end{tabular}}
\end{table}

>>>>

The linear predictor is composed of an intercept, $b_0$, covariates, $X$, and a vector of regression coefficients $\boldsymbol\beta$.
We also include a spatial, Gaussian random field, $u_s(\rho, \sigma_u)$ and a polygon-level iid random effect, $ v_a(\sigma_v)$.
$$\eta_b = \beta_0 + \boldsymbol\beta X  + u_s(\rho, \sigma_u) + v_a(\sigma_v) $$
The Gaussian spatial effect $u(s, \rho, \sigma_u)$ has a Mat\'ern covariance function and two hyper parameters: $\rho$, the nominal range on the longitude-latitude scale (beyond which correlation is $< 0.1$) and $\sigma_u$, the marginal standard deviation.
The iid random effect, $v_a \sim \operatorname{Normal}(0, \sigma_v)$,  was grouped by polygon, with all pixels within polygon $j$ being grouped together.
Internally, this effect is parameterised as the log of the precision, $\omega_v = \log(\tau_v) = \log(\frac{1}{{\sigma_v}^2})$ to improve numeric stability.
This random effect modelled both missing covariates and extra-Poisson sampling error.

@@

We assigned $\sigma_v$ a penalised complexity prior \citep{simpson2017penalising} such that $P(\sigma_v > 0.05) = 0.0000001$.
This was based on a comparison of the variance of Poisson random variables, with rates given by the number of cases observed, and an separately derived upper and lower bound for the case counts using the approach defined by Cibulskis and colleagues \citep{cibulskis2011worldwide}.
We found that an iid effect with a standard deviation of 0.05 was able to account for the discrepancy between the assumed Poisson error and the separately derived measurement error.

@@

$$\eta_b = \beta_0 + \mathbf{1}_p\beta_p +  \boldsymbol\beta X  + u_s(\rho, \sigma_u) + v_a(\sigma_v) + w_b(\sigma_w).$$
As well as the global intercept, $\beta_0$, this model has a prevalence survey specific intercept $b_p$ where the indicator function, $\mathbf{1}_p$ denotes that this term is zero except when a prevalence point-survey is being considered.
The iid random effect, $v_a \sim \operatorname{Norm}(0, \sigma_v)$, was again grouped by polygon, with all pixels and point-surveys within polygon $a$ being in the same group as polygon $a$.
The second iid random effect, $w_b \sim \operatorname{Normal}(0, \sigma_w)$, was applied to each point-survey.
To improve numeric stability this effect is also parameterised internally as the log of the precision, $\omega_w = \log(\tau_w) = \log(\frac{1}{{\sigma_w}^2})$.
This effect modelled extra-binomial sampling noise.
As such, this random effect is not included in the predicted uncertainty in the incidence or prevalence layers.

@@

\begin{table}
\caption{\label{table1}Summary of out-of-sample accuracy for all cross-validation experiments. 
Mean absolute error of predicted incidence rate against out-of-sample observed data for three countries.}
\centering
\fbox{%
\begin{tabular}{*{5}{l}}
{\bf Cross-validation} & {\bf Country}  & {\bf Baseline} & {\bf Prev GP} & {\bf Joint} \\
\hline
Random & Indonesia  & 13.95 &  14.09 &  {\bf 13.79}\\
& Senegal  & 12.41 &  {\bf 12.37} &  13.07\\
& Madagascar  & 39.06 &  {\bf 35.82} &  36.36\vspace{3mm}\\
Spatial & Indonesia & {\bf 14.77} &  {\bf 14.77} &  16.46\\
& Senegal  & 13.09 &  {\bf 12.21} &  15.15\\
& Madagascar & 67.73 &  50.38 &  {\bf 44.05}\\
\end{tabular}}
\end{table}

@@
